---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)


data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
```


# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR.

The remainder of this paper is structured as follows. @sec-data....



# Data {#sec-data}


And also planes (@fig-planes).

```{r}
#| label: fig-planes
#| fig-cap: Relationship between date and marriage
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point(alpha = 0.8)
  
```

Talk way more about it. 


# Results


# Discussion

## First discussion point {#sec-first-point}

## Second discussion point

## Third discussion point

## Weaknesses and next steps

\newpage

\appendix

# Appendix {-}


# Additional data details

# Model details {#sec-model-details}



\newpage


# References


